---
title: Project title
author: Ctrl Alt Elite
output: github_document
---

```{r load-packages}
library(tidyverse)
library(maps)
library(sf)
library(rnaturalearth)
library(rvest)
library(ggthemes)
library(lubridate)
library(stringr)
library(ggridges)
# cleanFun <- function(htmlString) {
#   return(gsub("<.*?>", "", htmlString))
# }
```

```{r set-default-figure-parameters}
knitr::opts_chunk$set(
  fig.width = 8, # 8"
  fig.asp = 0.618, # the golden ratio
  fig.retina = 3, # dpi multiplier for displaying HTML output on retina
  dpi = 300, # higher dpi, sharper image
  out.width = "90%"
)
```

```{r load-data-functions}
tweets <- read.csv("data/tweets.csv")
```

## Introduction

(1-2 paragraphs)
Brief introduction to the dataset.
You may repeat some of the information about the dataset provided in the introduction to the dataset on the TidyTuesday repository, paraphrasing on your own terms.
Imagine that your project is a standalone document and the grader has no prior knowledge of the dataset.

## Question 1 <- Update title to relate to the question you’re answering

### Introduction

(1-2 paragraphs)
Introduction to the question and what parts of the dataset are necessary to answer the question. Also discuss why you’re interested in this question.

### Approach

(1-2 paragraphs)
Describe what types of plots you are going to make to address your question.
For each plot, provide a clear explanation as to why this plot (e.g. boxplot, barplot, histogram, etc.) is best for providing the information you are asking about. 
The two plots should be of different types, and at least one of the two plots needs to use either color mapping or facets.

### Analysis

(2-3 code blocks, 2 figures, text/code comments as needed)
In this section, provide the code that generates your plots. Use scale functions to provide nice axis labels and guides.
You are welcome to use theme functions to customize the appearance of your plot, but you are not required to do so.
All plots must be made with ggplot2. Do not use base R or lattice plotting functions.

```{r question-one-plot-one-wrangling}
tweets_locations <- tweets %>% 
  filter(!str_detect(location, "@"), !str_detect(location, ":")) %>% 
  mutate(location_pre_comma = gsub(",.*","", location)) %>%
  mutate(location_pre_comma = case_when(
    location_pre_comma == "北京" ~ "Beijing",
    location_pre_comma == "God's earth" ~ "NA",
    location_pre_comma == "The City College of New York" ~ "New York",
    location_pre_comma == "World" ~ "NA",
    location_pre_comma == "he/they" ~ "NA",
    location_pre_comma == "At the home office" ~ "NA",
    location_pre_comma == "Deutschland" ~ "Germany",
    location_pre_comma == "Distrito Federal" ~ "Mexico City",
    location_pre_comma == "down in dey wid em" ~ "NA",
    location_pre_comma == "Forde-Obama Hall" ~ "NA",
    location_pre_comma == "France & UK" ~ "NA",
    location_pre_comma == "Lil’ Rudyshire" ~ "NA",
    location_pre_comma == "MIT" ~ "Boston",
    location_pre_comma == "New Yorker" ~ "New York",
    location_pre_comma == "OAK / NYC / ATL / The World" ~ "NA",
    location_pre_comma == "SP" ~ "NA",
    location_pre_comma == "Toronto || Ottawa" ~ "NA",
    location_pre_comma == "Tx" ~ "Texas",
    location_pre_comma == "UK" ~ "United Kingdom",
    location_pre_comma == "USA" ~ "United States",
    location_pre_comma == "Worldwide" ~ "NA",
    TRUE ~ location_pre_comma
  ))
  
tweets_locations <- tweets_locations %>%
  mutate(plot_state = case_when(
    location_pre_comma == "Nashville" ~ "Tennessee",
    location_pre_comma =="Merced" ~ "California",
    location_pre_comma == "Vienna" ~ "Austria",
    location_pre_comma == "Madison" ~ "Wisconsin",
    location_pre_comma == "Minneapolis" ~ "Minnesota",
    location_pre_comma == "Philadelphia" ~ "Pennsylvania",
    location_pre_comma == "Boston" ~ "Massachusetts",
    location_pre_comma == "London" ~ "United Kingdom",
    location_pre_comma == "Edinburgh" ~ "United Kingdom",
    location_pre_comma == "Amherst" ~ "Massachusetts",
    location_pre_comma == "Buffalo" ~ "New York",
    location_pre_comma == "Cambridge" ~ "Massachusetts",
    location_pre_comma == "San Diego" ~ "California",
    TRUE ~ as.character(location_pre_comma)
  ))

top_10_locations <- tweets_locations %>%
  count(plot_state) %>%
  arrange(desc(n)) %>%
  filter(plot_state != "NA") %>%
  head(10) %>%
  mutate(internat = case_when(
    plot_state == "United Kingdom" ~ "International",
    plot_state == "Austria" ~ "International",
    TRUE ~ "Domestic"),
    plot_state = fct_reorder(plot_state, n),
    percent_tweets = paste(round(n / sum(n), 4) * 100, "%"))
```

```{r question-one-plot-one}
ggplot(data = top_10_locations, aes(y = plot_state, x = n, fill = internat)) +
  geom_col() +
  geom_text(aes(label = percent_tweets, color = internat), 
            size = 2.5,
            nudge_x = 8, 
            show.legend = FALSE) +
  scale_fill_colorblind() +
  scale_color_colorblind() +
  scale_x_continuous(breaks = c(0, 20, 40, 60, 80, 100, 120, 140, 160, 180, 200)) +
  labs(
    y = "Region",
    x = "Number of Tweets",
    title = "Top 10 Most Popular #DuBoisChallenge Tweet Locations",
    fill = "Location"
  ) +
  theme_minimal() +
  theme(text = element_text(family = "Times New Roman"))
```

```{r question-one-plot-two-wrangling}
northeast_tweets <- tweets %>%
  filter(long <= -70,
         long >= -90,
         lat <= 46,
         lat >= 20)

europe_tweets <- tweets %>% 
  filter(long >= -20 & long <= 45,
         lat >= 30 & lat <= 73)
```

```{r question-one-plot-two-map-df}
# world map/eu code taken from https://www.r-bloggers.com/2019/04/zooming-in-on-maps-with-sf-and-ggplot2/
world_map <- ne_countries(scale = 'medium', type = 'map_units',
                         returnclass = 'sf')
us_map <- map_data("state")
canada_map <- map_data("world","canada")
```

```{r question-one-plot-two, warning = FALSE}
# Add labels for states and Europe countries

# Do we need to address showing relative populations like we said we would in 
# proposal cause of peer feedback??

# Need to address why there are so many tweets from NY twitter location but
# based on long lat there are hardly any in NY in map

ggplot() +
  geom_polygon(data = canada_map, 
               aes(x = long, y = lat, group = group), 
               fill = "lightgray", 
               color = "black") +
  geom_polygon(data = us_map, 
               aes(x = long, y = lat, group = group), 
               fill = "lightgray", color = "black") +
  geom_point(data = northeast_tweets, 
             aes(x = long, y = lat, size = retweet_count, alpha = retweet_count), 
             color = "red") +
  coord_map(xlim = c(-80, -65),
            ylim = c(36, 46)) +
  scale_alpha_continuous(range = c(.4, 1)) +
  labs(title = "#DuBoisChallenge Tweets in the North-East and Canada",
       size = "Number of Retweets",
       alpha = "Number of Retweets") +
  theme_minimal() +
  theme_void() +
  theme(text = element_text(family = "Times New Roman"))

ggplot() + 
  geom_sf(data = world_map, fill = "lightgray", color = "black") +
  geom_point(data = europe_tweets, 
             aes(x = long, y = lat, size = retweet_count, alpha = retweet_count), 
             color = "red") +
  scale_alpha_continuous(range = c(.4, 1)) +
  labs(title = "#DuBoisChallenge Tweets in Europe",
       size = "Number of Retweets",
       alpha = "Number of Retweets") +
  theme_void() +
  coord_sf(xlim = c(-20, 45), ylim = c(30, 73), expand = FALSE) +
  theme(text = element_text(family = "Times New Roman"))
```

### Discussion

(1-3 paragraphs)
In the Discussion section, interpret the results of your analysis. Identify any trends revealed (or not revealed) by the plots.
Speculate about why the data looks the way it does.

## Question 2 <- Update title to relate to the question you’re answering

The second question we want to answer is: 

*How does the tweet timing affect user construction of #DuBois 
challenge tweets and how the audience reacts to those tweets?*

### Introduction

(1-2 paragraphs)
Introduction to the question and what parts of the dataset are necessary to answer the question. Also discuss why you’re interested in this question.

### Approach

(1-2 paragraphs)
Describe what types of plots you are going to make to address your question.
For each plot, provide a clear explanation as to why this plot (e.g. boxplot, barplot, histogram, etc.) is best for providing the information you are asking about. 
The two plots should be of different types, and at least one of the two plots needs to use either color mapping or facets.

### Analysis

(2-3 code blocks, 2 figures, text/code comments as needed)
In this section, provide the code that generates your plots. Use scale functions to provide nice axis labels and guides.
You are welcome to use theme functions to customize the appearance of your plot, but you are not required to do so.
All plots must be made with ggplot2. Do not use base R or lattice plotting functions.

```{r question-two-plot-one-wrangling}
tweets_time <- tweets %>% 
  filter(!is.na(datetime)) %>%
  mutate(tag_count = str_count(content, "@"),
         time = as.numeric(str_sub(datetime, start=12, end=13)),
         date = ymd(str_sub(datetime, start = 1, end = 11)),
         month = month(date),
         month_name = case_when(
           month == 2 ~ "February",
           month == 3 ~ "March",
           month == 4 ~ "April",
           month == 5 ~ "May"),
         month_name = fct_reorder(month_name, month)
         )
```

```{r question-two-plot-one}
tweets_time %>% 
  filter(month_name != "May") %>% 
ggplot(aes(x = month_name, y = tag_count, color = month_name)) + 
  geom_boxplot(show.legend = FALSE) +
  scale_color_colorblind() +
  scale_y_continuous(breaks = c(0, 2, 4, 6, 8, 10, 12)) +
  labs(
    x = "Month Tweeted",
    y = "Number of People Tagged",
    title = "When #DuBoisChallenge Tweeters Tagged People"
  ) +
  theme(text = element_text(family = "Times New Roman"))
```

```{r question-two-plot-two}
tweets_time %>% 
  filter(month_name != "May") %>% 
ggplot(aes(x = like_count)) + 
  facet_wrap(~ month_name, scales = "free_x") +
  geom_histogram() +
  scale_color_colorblind() 
```
### Discussion

(1-3 paragraphs)
In the Discussion section, interpret the results of your analysis. Identify any trends revealed (or not revealed) by the plots.
Speculate about why the data looks the way it does.

## Presentation

Our presentation can be found [here](presentation/presentation.html).

## Data 

Include a citation for your data here. 
See http://libraryguides.vu.edu.au/c.php?g=386501&p=4347840 for guidance on proper citation for datasets. 
If you got your data off the web, make sure to note the retrieval date.

## References

List any references here. You should, at a minimum, list your data source.
