---
title: Twitter Trends from the \#DuBoisChallenge
author: by Ctrl+Alt+Elite
output: github_document
editor_options: 
  chunk_output_type: inline
---

```{r load-packages, message = FALSE}
# Package messages suppressed
library(tidyverse)
library(maps)
library(sf)
library(rnaturalearth)
library(rvest)
library(ggthemes)
library(lubridate)
library(stringr)
library(colorspace)
library(scales)
library(ggrepel)
library(RColorBrewer)
```

```{r set-default-figure-parameters}
knitr::opts_chunk$set(
  fig.width = 8,
  fig.asp = 0.618,
  fig.retina = 3,
  dpi = 300,
  out.width = "90%"
)
```

```{r load-data}
tweets <- read.csv("data/tweets.csv")
```

## Introduction

(1-2 paragraphs)
Brief introduction to the dataset.
You may repeat some of the information about the dataset provided in the introduction to the dataset on the TidyTuesday repository, paraphrasing on your own terms.
Imagine that your project is a standalone document and the grader has no prior knowledge of the dataset.

```{r glimpse-data, echo = FALSE}
glimpse(tweets)
```

W.E.B DuBois was a famed data visualisation expert who conducted data analysis 
to challenge the racist notions regarding African Americans in the early 20th
century. The #DuBoisChallenge celebrates the legacy of W.E.B DuBois by 
encouraging users to creatively recreate various visualizations from the 1900
Paris Exposition using modern data visualization tools. 

For our dataset (tweets), we have chosen to examine the 2021 WEB Du Bois & 
Juneteenth Twitter data where each observation is a tweet from 2021 that uses 
the DuBoisChallenge hashtag, and the variables are the accompanying metadata 
such as likes, retweets, and location. The dataset includes `r ncol(tweets)` 
different variables and a total of `r nrow(tweets)` observations. The data was 
collected via scraping from Twitter based on the presence of the WEB Du Bois 
challenge hashtag. 

The following variables are included in the data set:

- `datetime` (double): Date and time of tweet
- `content`	(character): Text for tweet
- `retweet_count` (double): Retweet count for tweet
- `like_count` (double): Like count for tweet
- `quote_count`	(double): Quote tweet count for tweet
- `text` (character): Where tweet was posted from
- `username` (character): Username of Tweeter
- `location` (character): Location tweeted from
- `followers` (double): Followers of the tweeter
- `url` (character): Canonical url of tweet
- `verified` (logical): Is user verified?
- `lat` (double): Latitude of user
- `long` (double): Longitude of user

## Question 1 <- Update title to relate to the question you’re answering

### Introduction

(1-2 paragraphs)
Introduction to the question and what parts of the dataset are necessary to 
answer the question. Also discuss why you’re interested in this question.

Since users in this challenge were from all across the world we wanted to create
visualizations to gauge interest and participation by geographical locations.
Specifically, there are 2 ways that we operationalized geographical locations:
home location provided manually by the twitter user (`lat`and `long`) and the 
location at time of tweet (`location`). We wanted to quantify geographical 
interest by the number of retweets (`retweet_count`) and number of tweets coming
from a given location (mutated variable - n), which we will use as our
dependent variables in the 2 visualizations. 

The reason we were very interested in this questions is because we assumed that
DuBois' work would mostly be studied and know by Americans, as it depicts 
experiences of African Americans. However, since people are participating in
the TidyTuesday challenge across the globe, we wanted to understand if and where 
there is widespread interest in DuBois' work from an international perspective.


### Approach

(1-2 paragraphs)
Describe what types of plots you are going to make to address your question.
For each plot, provide a clear explanation as to why this plot (e.g. boxplot, barplot, histogram, etc.) is best for providing the information you are asking about. 
The two plots should be of different types, and at least one of the two plots needs to use either color mapping or facets.

For our 1st visualization, we wanted to understand what the most popular 
locations at the time of tweets were for the #DuBoisChallenge. To do so, we 
first cleaned the `location` column to ensure that we only had valid locations.
For a few cases, we had to manually either drop the data point or rename them
appropriately. After this, we added the corresponding state/international 
country for each data point in the `location` column. We then ranked the top 10
states/international countries (excluding NA's) based on the number of total 
acuumulated in that location. To visualize this, we decided to utilize a bar 
plot since it is easy to visualize the number of tweets from locations in 
descending order. We also decided to fill the bars based on if they were in the
US or not, which allows users to distinguish the different types of locations. 
We also decided to state the percentages on top of each bar plot to make it 
more intuitive and accessible. 

For our 2nd visualization, we wanted to physically map out the trends in terms
of the home locations of the twitter users. Based on the results of our 1st 
visualization, we wanted to specifically look into the locations that seemed to
be the most active in terms tweeting with the #DuBoisChallenge. Since we had
`lat` and `long`, we wanted to visualize these points on a map, so that we could
have more precise home locations of the twitter users and readers can better
spatially understand participation across the world. We also wanted to 
understand the sharing of tweets, and therefore, we sized each point on the map
based on `retweet_count`. 

### Analysis

(2-3 code blocks, 2 figures, text/code comments as needed)
In this section, provide the code that generates your plots. Use scale functions to provide nice axis labels and guides.
You are welcome to use theme functions to customize the appearance of your plot, but you are not required to do so.
All plots must be made with ggplot2. Do not use base R or lattice plotting functions.

```{r question-one-wrangling}
tweets <- tweets %>%
  mutate(tag_count = str_count(content, "@"))

tweets_locations <- tweets %>%
  filter(!str_detect(location, "@"), !str_detect(location, ":")) %>%
  mutate(
    location_pre_comma = gsub(",.*", "", location),
    location_pre_comma = case_when(
      location_pre_comma == "北京" ~ "Beijing",
      location_pre_comma == "God's earth" ~ "NA",
      location_pre_comma == "The City College of New York" ~ "New York",
      location_pre_comma == "World" ~ "NA",
      location_pre_comma == "he/they" ~ "NA",
      location_pre_comma == "At the home office" ~ "NA",
      location_pre_comma == "Deutschland" ~ "Germany",
      location_pre_comma == "Distrito Federal" ~ "Mexico City",
      location_pre_comma == "down in dey wid em" ~ "NA",
      location_pre_comma == "Forde-Obama Hall" ~ "NA",
      location_pre_comma == "France & UK" ~ "NA",
      location_pre_comma == "Lil’ Rudyshire" ~ "NA",
      location_pre_comma == "MIT" ~ "Boston",
      location_pre_comma == "New Yorker" ~ "New York",
      location_pre_comma == "OAK / NYC / ATL / The World" ~ "NA",
      location_pre_comma == "SP" ~ "NA",
      location_pre_comma == "Toronto || Ottawa" ~ "NA",
      location_pre_comma == "Tx" ~ "Texas",
      location_pre_comma == "UK" ~ "United Kingdom",
      location_pre_comma == "USA" ~ "United States",
      location_pre_comma == "Worldwide" ~ "NA",
      TRUE ~ location_pre_comma
    ),
    plot_state = case_when(
      location_pre_comma == "Nashville" ~ "Tennessee",
      location_pre_comma == "Merced" ~ "California",
      location_pre_comma == "Vienna" ~ "Austria",
      location_pre_comma == "Madison" ~ "Wisconsin",
      location_pre_comma == "Minneapolis" ~ "Minnesota",
      location_pre_comma == "Philadelphia" ~ "Pennsylvania",
      location_pre_comma == "Boston" ~ "Massachusetts",
      location_pre_comma == "London" ~ "United Kingdom",
      location_pre_comma == "Edinburgh" ~ "United Kingdom",
      location_pre_comma == "Amherst" ~ "Massachusetts",
      location_pre_comma == "Buffalo" ~ "New York",
      location_pre_comma == "Cambridge" ~ "Massachusetts",
      location_pre_comma == "San Diego" ~ "California",
      TRUE ~ as.character(location_pre_comma)
    )
  )

top_10_locations <- tweets_locations %>%
  count(plot_state) %>%
  arrange(desc(n)) %>%
  filter(plot_state != "NA") %>%
  head(10) %>%
  mutate(
    region = case_when(
      plot_state == "New York" ~ "US: Northeast",
      plot_state == "New Jersey" ~ "US: Northeast",
      plot_state == "Pennsylvania" ~ "US: Northeast",
      plot_state == "Massachusetts" ~ "US: Northeast",
      plot_state == "Tennessee" ~ "US: South",
      plot_state == "California" ~ "US: West",
      plot_state == "Austria" ~ "Europe",
      plot_state == "United Kingdom" ~ "Europe",
      plot_state == "Wisconsin" ~ "US: Midwest",
      plot_state == "Minnesota" ~ "US: Midwest"
    ),
    region = fct_relevel(region, c(
      "US: Northeast", "Europe", "US: Midwest", "US: South",
      "US: West"
    )),
    plot_state = fct_relevel(plot_state, c(
      "New York", "New Jersey", "Massachusetts",
      "Pennsylvania", "Austria", "United Kingdom",
      "Minnesota",
      "Wisconsin", "Tennessee", "California"
    )),
    plot_state = fct_rev(plot_state),
    percent_tweets = paste(round(n / sum(n), 4) * 100, "%")
  )

northeast_tweets <- tweets %>%
  filter(
    long <= -70,
    long >= -90,
    lat <= 46,
    lat >= 20
  )
europe_tweets <- tweets %>%
  filter(
    long >= -20 & long <= 45,
    lat >= 30 & lat <= 73
  )

world_map <- ne_countries(
  scale = "medium", type = "map_units",
  returnclass = "sf"
)
us_map <- map_data("state")
canada_map <- map_data("world", "canada")

US_locations <- tribble(
  ~city, ~lat, ~long,
  "NYC", 40.7128, -74.0060,
  "Baltimore", 39.2904, -76.6122
)

EU_locations <- tribble(
  ~city, ~lat, ~long,
  "London", 51.5074, -0.1278,
  "Vienna", 48.2082, 16.3738,
  "Rome", 41.9028, 12.4964
)
```

```{r question-one-plot-one, fig.align = 'center'}
ggplot(data = top_10_locations, aes(y = plot_state, x = n, fill = region)) +
  geom_col() +
  geom_text(aes(label = percent_tweets, color = region),
    size = 2.5,
    nudge_x = 8,
    show.legend = FALSE
  ) +
  scale_fill_brewer(palette = "Set1") +
  scale_color_brewer(palette = "Set1") +
  scale_x_continuous(
    breaks = c(0, 20, 40, 60, 80, 100, 120, 140, 160, 180, 200)
  ) +
  labs(
    title = "Top 10 #DuBoisChallenge Tweet Locations",
    caption = "% calculated out of top 10",
    x = "Number of Tweets",
    y = "User Location in Twitter Bio",
    fill = "Location"
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold"),
    plot.caption = element_text(face = "italic"),
    legend.title = element_blank(),
    legend.position = c(.848, .25),
    text = element_text(family = "Times New Roman")
  )
```

```{r question-one-plot-two, warning = FALSE, fig.align = 'center'}
set.seed(1234)

ggplot() +
  geom_polygon(
    data = canada_map,
    aes(x = long, y = lat, group = group),
    fill = "#F0F0F0",
    color = "black"
  ) +
  geom_polygon(
    data = us_map,
    aes(x = long, y = lat, group = group),
    fill = "#F0F0F0", color = "black"
  ) +
  geom_jitter(
    data = northeast_tweets,
    width = 0.5, height = .5,
    aes(
      x = long, y = lat, size = tag_count, color = tag_count,
      alpha = tag_count
    )
  ) +
  labs(
    title = "#DuBoisChallenge Tweets",
    subtitle = "in Northeastern U.S. & Canada\n",
    caption = "Based on Location Where Tweet Was Published",
    size = "# of Users Tagged",
    color = "# of Users Tagged",
    alpha = "# of Users Tagged"
  ) +
  theme_void() +
  scale_color_continuous_sequential(
    palette = "OrYel", rev = FALSE,
    breaks = c(0, 2, 4, 6, 8, 10)
  ) +
  scale_size_continuous(range = c(2, 5), breaks = c(0, 2, 4, 6, 8, 10)) +
  scale_alpha_continuous(range = c(.27, 1), breaks = c(0, 2, 4, 6, 8, 10)) +
  guides(
    color = guide_legend(),
    size = guide_legend(),
    alpha = guide_legend()
  ) +
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold"),
    plot.subtitle = element_text(hjust = 0.5, face = "italic"),
    plot.caption = element_text(hjust = 0.5),
    legend.position = "bottom",
    panel.border = element_rect(color = "black", fill = NA, size = .75),
    panel.background = element_rect(color = "black", fill = "lightblue"),
    text = element_text(family = "Times New Roman")
  ) +
  geom_text_repel(
    data = US_locations,
    aes(x = long, y = lat, label = city),
    size = 3, nudge_x = -0.15,
    nudge_y = 0.95,
    segment.linetype = "dotted"
  ) +
  coord_map(
    xlim = c(-80, -65),
    ylim = c(36, 46)
  )

ggplot() +
  geom_sf(data = world_map, fill = "#F0F0F0", color = "black") +
  geom_jitter(
    data = europe_tweets,
    aes(
      x = long, y = lat, size = tag_count, color = tag_count,
      alpha = tag_count
    )
  ) +
  coord_sf(xlim = c(-20, 45), ylim = c(30, 73), expand = FALSE) +
  labs(
    title = "#DuBoisChallenge Tweets",
    subtitle = "in Europe\n",
    caption = "Based on Location Where Tweet Was Published",
    size = "# of Users Tagged",
    alpha = "# of Users Tagged",
    color = "# of Users Tagged"
  ) +
  theme_void() +
  scale_color_continuous_sequential(
    palette = "OrYel", rev = FALSE,
    breaks = c(0, 2, 4, 6, 8, 10)
  ) +
  scale_size_continuous(range = c(2, 5), breaks = c(0, 2, 4, 6, 8, 10)) +
  scale_alpha_continuous(range = c(.27, 1), breaks = c(0, 2, 4, 6, 8, 10)) +
  guides(
    color = guide_legend(),
    size = guide_legend(),
    alpha = guide_legend()
  ) +
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold"),
    plot.subtitle = element_text(hjust = 0.5, face = "italic"),
    plot.caption = element_text(hjust = 0.5),
    legend.position = "bottom",
    panel.border = element_rect(color = "black", fill = NA, size = .75),
    panel.background = element_rect(color = "black", fill = "lightblue"),
    text = element_text(family = "Times New Roman")
  ) +
  geom_text_repel(
    data = EU_locations,
    aes(x = long, y = lat, label = city),
    size = 3,
    nudge_x = -14, nudge_y = -0.3,
    segment.linetype = "dotted"
  )
```

### Discussion

(1-3 paragraphs)
In the Discussion section, interpret the results of your analysis. Identify any trends revealed (or not revealed) by the plots.
Speculate about why the data looks the way it does.

## Question 2 <- Update title to relate to the question you’re answering

The second question we want to answer is: 

*How does the tweet timing affect user construction of #DuBois 
challenge tweets and how the audience reacts to those tweets?*

### Introduction

(1-2 paragraphs)
Introduction to the question and what parts of the dataset are necessary to answer the question. Also discuss why you’re interested in this question.

### Approach

(1-2 paragraphs)
Describe what types of plots you are going to make to address your question.
For each plot, provide a clear explanation as to why this plot (e.g. boxplot, barplot, histogram, etc.) is best for providing the information you are asking about. 
The two plots should be of different types, and at least one of the two plots needs to use either color mapping or facets.

### Analysis

(2-3 code blocks, 2 figures, text/code comments as needed)
In this section, provide the code that generates your plots. Use scale functions to provide nice axis labels and guides.
You are welcome to use theme functions to customize the appearance of your plot, but you are not required to do so.
All plots must be made with ggplot2. Do not use base R or lattice plotting functions.

```{r question-two-plot-one-wrangling}
tweets <- tweets %>%
  mutate(devicetype = case_when(
    str_detect(text, "Twitter Web App") ~ "Web App",
    str_detect(text, "Twitter for iPhone") ~ "iPhone",
    str_detect(text, "Twitter for Android") ~ "Android",
    str_detect(text, "Buffer") ~ "Buffer",
    str_detect(text, "Twitter for iPad") ~ "iPad",
    str_detect(text, "TweetDeck") ~ "TweetDeck",
    str_detect(text, "Crowdfire App") ~ "Crowdfire App",
    str_detect(text, "Twitter for Mac") ~ "Mac"
  ))

tweets_device <- tweets %>%
  filter(devicetype == "iPhone" |
    devicetype == "Web App" |
    devicetype == "Android")

users_and_devicetype <- tweets %>%
  group_by(username) %>%
  select(username, devicetype) %>%
  count(devicetype) %>%
  arrange(desc(n)) %>%
  slice(1) %>%
  select(-n)

users_and_avg_follower <- tweets %>%
  group_by(username) %>%
  summarise(avg_followers = mean(followers))

joined_devices_follower <- inner_join(users_and_devicetype,
  users_and_avg_follower,
  by = "username"
) %>%
  filter(devicetype == "iPhone" |
    devicetype == "Web App" |
    devicetype == "Android")
```

```{r question-two-plot-one, warning = FALSE, fig.align = 'center'}
# Plot drops NAs and tweets with 0 likes since log(0) is undefined
ggplot(data = tweets_device, aes(x = like_count, fill = devicetype)) +
  facet_wrap(~devicetype, ncol = 1) +
  geom_boxplot(show.legend = FALSE) +
  scale_fill_manual(values = c("#a4c639", "#A2AAAD", "#1DA1F2")) +
  scale_x_log10() +
  labs(
    title = "Distribution of Likes",
    subtitle = "by Device Tweet Was Posted From",
    caption = "x-axis uses logarithmic scale (tweets with 0 likes are ommited)",
    x = "Number of Likes",
    y = NULL 
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold"),
    plot.subtitle = element_text(hjust = 0.5, face = "italic"),
    plot.caption = element_text(face = "italic", hjust = 0.5),
    axis.ticks = element_blank(),
    axis.text.y = element_blank(),
    text = element_text(family = "Times New Roman")
  )
```

```{r question-two-plot-two, warning = FALSE, fig.align = 'center'}
# Plot drops NAs and tweets with 0 likes since log(0) is undefined
ggplot(
  data = joined_devices_follower,
  aes(x = avg_followers, fill = devicetype)
) +
  geom_density(show.legend = FALSE) +
  facet_wrap(. ~ devicetype, nrow = 3) +
  theme_minimal() +
  scale_x_log10(labels = label_number(big.mark = ",")) +
  scale_fill_manual(values = c("#a4c639", "#A2AAAD", "#1DA1F2")) +
  scale_y_continuous(labels = label_number(accuracy = .1)) +
  labs(
    title = "Distribution of Follower Count",
    subtitle = "by User's Primary Device",
    caption = "x-axis uses logarithmic scale", 
    x = "Average Number of Followers Per User",
    y = NULL
  ) +
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold"),
    plot.subtitle = element_text(hjust = 0.5, face = "italic"),
    plot.caption = element_text(face = "italic"),
    text = element_text(family = "Times New Roman")
  )
```

### Discussion

(1-3 paragraphs)
In the Discussion section, interpret the results of your analysis. Identify any trends revealed (or not revealed) by the plots.
Speculate about why the data looks the way it does.

## Presentation

Our presentation can be found [here](presentation/presentation.html).

## Data 

Starks, A, Hillery, A, Tyler, S 2021, *Du Bois and Juneteenth revisited: 
TidyTuesday week 8 of 2021*, electronic dataset, tidytuesday, retrieved 13 
September 2021, 
<https://github.com/rfordatascience/tidytuesday/blob/master/data/2021/2021-06-15/readme.md>.

## References

[Data Source](https://github.com/rfordatascience/tidytuesday/blob/master/data/2021/2021-06-15/readme.md)

[Grammarly Article](https://www.theladders.com/career-advice/study-you-make-5-times-as-many-errors-writing-on-your-phone-than-on-your-computer)

[Android Logo Color](https://encycolorpedia.com/a4c639#:~:text=The%20hexadecimal%20color%20code%20%23a4c639,%25%20green%20and%2022.35%25%20blue.)

[Apple Logo Color](https://www.brandcolorcode.com/apple)

[Twitter Logo Color](https://www.onlinepalette.com/twitter/#:~:text=Twitter%20uses%20the%20colors%20blue,29%2C%20161%2C%20242)

[Europe Map](https://www.r-bloggers.com/2019/04/zooming-in-on-maps-with-sf-and-ggplot2/)

[Latitude and Longitude of Cities](https://www.google.com/maps)