---
title: "Project proposal"
author: "ctrl_alt_elite"
output: github_document
---

```{r load-packages, message = FALSE}
library(tidyverse)
```

```{r load-data, message = FALSE, warning = FALSE}
tweets <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2021/2021-06-15/tweets.csv')
glimpse(tweets)
```


## Dataset

Our dataset was collected from: https://github.com/rfordatascience/tidytuesday/blob/master/data/2021/2021-06-15/readme.md

For our dataset (Tweets), we have chosen to examine the 2021 WEB Du Bois & Juneteenth Twitter data where each observation is a tweet and the accompanying metadata such as likes, retweets, and location. The dataset includes `r ncol(tweets)` different variables and a total of `r nrow(tweets)` observations. The data was collected via scraping from Twitter based on the presence of the WEB Du Bois challenge hashtag. 

We chose this dataset because we appreciate the importance of celebrating W.E.B 
DuBois’s legacy in data visualization. The #DuBois challenge was a Tidy Tuesday 
challenge that asked users to recreate his 1900 Paris Exposition today. This 
exposition included visualizations that described the income, wealth, 
employment, and mobility of African Americans during this time period. By 
recreating these visualizations through the #DuBois challenge, users were able 
to understand the conditions of former slaves in the United States and honor the legacy and the progress of this group. Additionally, these sorts of 
visualizations are crucial to understanding modern-day issues in marginalized 
groups. From this data, we hope to learn how people engage with history and data visualization in a social media setting. 

We also chose the dataset because it is comprehensive to work with. There are a 
variety of different types of variables that can be used for analysis - logical, 
double, and character - and the dataset is well-cleaned. Since the data set is 
extensive, we know we will be able to answer a variety of non-overlapping 
questions that are pertinent to the world we live in today.

## Questions and Analysis Plan

### Question One

The first question we want to answer is “How does general interest of the #DuBois 
challenge vary geographically?” In order to explore this inquiry, we will use 
the `latitude`, `longitude`, and `retweet_count `variables. To display the 
geographical distribution of the data, we will use an external map of the world, 
on which we will layer a scatterplot of the location of each tweet. We will use 
the latitude and longitude variables to accomplish this, along with the world 
map coordinates that come from the map_data() function in tidyverse. Then, we 
will display the count of retweets for each tweet by mapping the `retweet_count` 
variable to color, size, or another scatterplot aesthetic, such that all of the 
information is very clearly displayed on the world map. 

### Question Two

The second question we want to answer is “How do the number of likes and 
followers of a Twitter user vary based on user verification status?” We will use 
the variables `followers`, `verified` and `like_count`. We will map `followers` 
to the x axis, and `like_count` to the y axis, and then display each point using 
geom_point. Then, we will use an aesthetic such as color or shape to map the 
verification status of the tweet author, such that viewers can easily 
distinguish the two groups. We will also employ geom_smooth to point out 
noticeable trend lines, and how they differ between verified and unverified users. 

