---
title: "Project proposal"
author: "ctrl_alt_elite"
output: github_document
---

```{r load-packages, message = FALSE}
library(tidyverse)
```

```{r load-data}
tweets <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2021/2021-06-15/tweets.csv')
glimpse(tweets)
```


## Dataset
For our dataset, we have chosen to examine the 2021 WEB Du Bois & Juneteenth Twitter data where each observation is a tweet and the accompanying metadata such as likes, retweets, and location. The dataset includes 13 different variables and a total of 445 observations. The data was collected via scraping from Twitter based on the presence of the WEB Du Bois challenge hashtag. 

We chose this dataset because we appreciate the importance of celebrating W.E.B DuBois’s legacy in data visualization. The #DuBois challenge was a Tidy Tuesday challenge that asked users to recreate his 1900 Paris Exposition today. This exposition included visualizations that described the income, wealth, employment, and mobility of African Americans during this time period. By recreating these visualizations through the #DuBois challenge, users were able to understand the conditions of former slaves in the United States and honor the legacy and the progress of this group. Additionally, these sorts of visualizations are crucial to understanding modern-day issues in marginalized groups. From this data, we hope to learn how people engage with data visualization in a social media setting.

We also chose the dataset because it is comprehensive to work with. There are a variety of different types of variables - logical, double, and character - and the dataset is well-cleaned. 


## Questions

The two questions you want to answer.

## Analysis plan

A plan for answering each of the questions including the variables involved, variables to be created (if any), external data to be merged in (if any).
