---
title: "Project proposal"
author: "ctrl_alt_elite"
output: github_document
---

```{r load-packages, message = FALSE, warning = FALSE}
library(tidyverse)
```

```{r load-data, message = FALSE, warning = FALSE}
tweets <- readr::read_csv(
  "https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2021/2021-06-15/tweets.csv"
)
```

## Dataset

Our dataset was collected from [the tidytuesday GitHub Repository of 
DuBoisChallenge tweets](https://github.com/rfordatascience/tidytuesday/blob/master/data/2021/2021-06-15/readme.md).

```{r glimpse-data}
glimpse(tweets)
```

For our dataset (Tweets), we have chosen to examine the 2021 WEB Du Bois & 
Juneteenth Twitter data where each observation is a tweet that uses the 
DuBoisChallenge hastag, and the accompanying metadata such as likes, retweets, 
and location. The dataset includes `r ncol(tweets)` different variables and a 
total of `r nrow(tweets)` observations. The data was collected via scraping from 
Twitter based on the presence of the WEB Du Bois challenge hashtag. 

The following variables are included in the data set:

- `datetime` (double): Date and time of tweet
- `content`	(character): Text for tweet
- `retweet_count` (double): Retweet count for tweet
- `like_count` (double): Like count for tweet
- `quote_count`	(double): Quote tweet count for tweet
- `text` (character): Where tweet was posted from
- `username` (character): Username of Tweeter
- `location` (character): Location tweeted from
- `followers` (double): Followers of the tweeter
- `url` (character): Canonical url of tweet
- `verified` (logical): Is user verified?
- `lat` (double): Latitude of user
- `long` (double): Longitude of user

We chose this dataset because we appreciate the importance of celebrating W.E.B 
DuBois’s legacy in data visualization. The #DuBois challenge was a Tidy Tuesday 
challenge that asked users to recreate his 1900 Paris Exposition today. This 
exposition included visualizations that described the income, wealth, employment, 
and mobility of African Americans during this time period. By recreating these 
visualizations through the #DuBois challenge, users were able to understand the 
conditions of former slaves in the United States and honor the legacy and the 
progress of this group. Additionally, these sorts of visualizations are crucial 
to understanding modern-day issues in marginalized groups. From this data, we 
hope to learn how people engage with history and data visualization in a social 
media setting. 

We also chose this data set due to its ease of use; there are a 
variety of different types of variables that can be used for analysis - logical, 
double, and character - and the data is well-cleaned. Since the data set is 
extensive, we know we will be able to answer a variety of non-overlapping 
questions that are pertinent to the world we live in today.

## Questions and Analysis Plan

### Question One

The first question we want to answer is: 

*How does general interest of the #DuBois challenge vary geographically?* 

We will first create a bar plot that maps `location` on the y-axis and the 
number of tweets from that location on the x-axis. This will require creating a 
new variable `location_tweet_count`. Since a user in one location can tweet 
multiple times, we will only consider one tweet per user to look at geographical 
engagement of users on this plot. We will also need to mutate a new variable 
`location_state`, based off of `location`, where location names are modified to 
either be a state in the United States, or categorized as an international 
country. If there happen to be many international locations in the data set 
from different counties, we will consider having two bar plots - one for U.S. 
states, and one for other countries, so that the visualization does not become 
too overcrowded. We will also need to look through the location data to remove 
any observations which do not represent actual names of geographical locations. 
By looking at this data on a bar plot, we will be able to compare engagement 
in the TidyTuesday challenge geographically, to see which locations produced 
the most number of tweets. The advantage of using a bar plot is that each 
location is very distinguishable from the next, and the data can be ordered such 
that it's obvious visually which locations have many tweets, versus very few 
tweets. This will also inform our next visualization, as we will know which 
areas of the global map to emphasize. 

In order to next explore this inquiry, we will use the `lat`, `long`, and 
`retweet_count `variables. To display the geographical distribution of the data, 
we will use an external map of the world, on which we will layer a scatterplot 
of the location of each tweet. We will use the latitude and longitude variables 
to accomplish this, along with the world map coordinates that come from the 
map_data() function in tidyverse. Then, we will display the count of retweets 
for each tweet by mapping the `retweet_count` variable to color, size, or 
another scatterplot aesthetic, such that all of the information is very clearly 
displayed on the world map. Since it will be important to consider the 
population differences of the locations on the map when analyzing the occurrence 
of tweets, we will either include this information in our narrative, or color 
the world map by population, so that the information is readily available to 
viewers. Thus, this visualization will most likely employ color mapping. 

### Question Two

The second question we want to answer is: 

*How does Twitter verification status affect engagement with the audience and 
their receptiveness to tweet content?


For this first visualization, we will use the variables `followers`, `verified` 
and `like_count`. We will map `followers` to the x axis, and `like_count` to the
y axis, and then display each point using geom_point. Since some users may have 
tweeted multiple times, we will take calculate `average_like_count` per tweet 
for each user, and use that number. This means for users who only tweeted once, 
we will use the like count for that tweet, while for users who tweeted multiple 
times, we will use the average like count across all of their challenge tweets. 
Then, we will use color mapping to map the verification status of the tweet 
author, such that viewers can easily distinguish the two groups. Further, 
we'll display a geom_smooth regression line for verified and unverified users. 
With these lines, we'll be able to examine the interaction between verification 
& followers and its effect on the number of likes a tweet can generate. 

#### Idea for second visualization
For a second visualization, we will use `verified` and `content` to examine the 
length of tweets between verified and unverified users and how this length 
affects the tweet's ability to spread. First, we'll compute the length of the 
tweet's content and assign it to a numeric variable `tweet_length`. Then, 
we'll create a ridge plot to compare the densities of tweet lengths between
verified and unverified users. 



