---
title: "Project proposal"
author: "ctrl_alt_elite"
output: github_document
---

```{r load-packages, message = FALSE, warning = FALSE}
library(tidyverse)
```

```{r load-data, message = FALSE, warning = FALSE}
tweets <- read.csv("tweets_proposal.csv")
```

## Dataset

Our dataset was collected from [the tidytuesday GitHub Repository of 
DuBois Challenge tweets](https://github.com/rfordatascience/tidytuesday/blob/master/data/2021/2021-06-15/readme.md).

```{r glimpse-data}
glimpse(tweets)
```

For our dataset (tweets), we have chosen to examine the 2021 WEB Du Bois & 
Juneteenth Twitter data where each observation is a tweet from 2021 that uses 
the DuBoisChallenge hashtag, and the variables are the accompanying metadata 
such as likes, retweets, and location. The dataset includes `r ncol(tweets)` 
different variables and a total of `r nrow(tweets)` observations. The data was 
collected via scraping from Twitter based on the presence of the WEB Du Bois 
challenge hashtag. 

The following variables are included in the data set:

- `datetime` (double): Date and time of tweet
- `content`	(character): Text for tweet
- `retweet_count` (double): Retweet count for tweet
- `like_count` (double): Like count for tweet
- `quote_count`	(double): Quote tweet count for tweet
- `text` (character): Where tweet was posted from
- `username` (character): Username of Tweeter
- `location` (character): Location tweeted from
- `followers` (double): Followers of the tweeter
- `url` (character): Canonical url of tweet
- `verified` (logical): Is user verified?
- `lat` (double): Latitude of user
- `long` (double): Longitude of user

We chose this dataset because we appreciate the importance of celebrating W.E.B 
Du Bois’s legacy in data visualization. The #DuBois challenge was a Tidy Tuesday 
challenge that asked users to recreate his 1900 Paris Exposition today. This 
exposition included visualizations that described the income, wealth, 
employment, and mobility of African Americans during this time period. By 
recreating these visualizations through the #DuBois challenge, users were able 
to understand the conditions of former slaves in the United States and honor the 
legacy and the progress of this group. Additionally, these sorts of 
visualizations are crucial to understanding modern-day issues in marginalized 
groups. From this data, we hope to learn how people engage with history and data 
visualization in a social media setting. 

We also chose this data set due to its ease of use; there are a variety of 
different types of variables that can be used for analysis - logical, double, 
and character - and the data is well-cleaned. Since the data set is extensive, 
we know we will be able to answer a variety of non-overlapping questions that 
are pertinent to the world we live in today.

## Questions and Analysis Plan

### Question One

The first question we want to answer is: 

*How does general interest of the #DuBois challenge vary geographically?* 

We will first create a bar plot that maps `location` on the y-axis and the 
number of tweets from that location on the x-axis. This will require creating a 
new variable `location_tweet_count`. As a user in one location can tweet 
multiple times, we will consider all their tweets cumulatively to look at 
total geographical engagement of users on this plot. This is due to the fact 
that we consider multiple tweets by a user to be a sign of engagement, and thus 
want to understand engagement on the whole, versus on a per user basis. We will 
also need to mutate a new variable `location_state`, based off of `location`, 
where location names are modified to be a state in the United States, or 
categorized as an international country. If there happen to be many 
international locations in the data set from different counties, we will 
consider having two bar plots - one for U.S. states, and one for other 
countries, so that the visualization does not become too overcrowded. We could 
also only display the top 10 or so locations on the bar plot, if need be for 
simplification purposes (we do not want too much overwhelming info). We will 
also need to look through the location data to remove any observations which do
not represent actual names of geographical locations. By looking at this data 
and organizing it on a bar plot, we will be able to compare engagement in the 
TidyTuesday challenge geographically, to see which locations produced the most 
number of tweets. The advantage of using a bar plot is that each location is 
very distinguishable from the next, and the data can be ordered such that it's 
obvious visually which locations have many tweets, versus very few tweets coming 
from them. This will also inform our next visualization, as we will know which 
areas of the global map to emphasize, if need be.

To next explore this inquiry, we will use the `lat`, `long`, and `retweet_count` 
variables. To display the geographical distribution of the data, we will use an 
external map of the world, on which we will layer a scatter plot of the location 
of each tweet (where it was tweeted from). We will use the latitude and 
longitude variables to accomplish this, along with the world map coordinates 
that come from the map_data() function in tidyverse. Then, we will display the 
count of retweets for each tweet by mapping the `retweet_count` variable to 
color, size, or another scatterplot aesthetic, such that all of the information 
is very clearly displayed on the world map. Since it will be important to 
consider the population differences of the locations on the map when analyzing 
the occurrence of tweets, we will create a separate heatmap of the world 
(we will use external data of the 2021 population of the world's countries), to 
be displayed next to this map, to help readers take population discrepancies 
into account. Thus, this visualization will most likely employ color mapping. 

We employ a comprehensive analysis of geographical interest, as the first 
visualization looks at the location tweeted from, while the second visualization 
examines the location of the actual user, presumably based on their profile. 

### Question Two

The second question we want to answer is: 

*How does Twitter verification status affect user construction of #DuBois 
challenge tweets and how the audience reacts to those tweets?*

For the first visualization, we will use `verified` and `content` to examine the 
length of tweets of verified and unverified users. First, we'll compute the 
length of each tweet's content, operationalized by the number of characters, 
including spaces and emojis, in the tweet, and assign it to a numeric variable 
`tweet_length`. Then, we'll create a ridge plot to succinctly compare the 
densities of tweet lengths between verified and unverified users. After seeing 
how verified users might write their tweets differently, we would then like to 
look into how users react to their tweets. 

Thus, for a second visualization, we will use the variables `followers`, 
`verified` and `like_count`. We will map `followers` to the x axis, and 
`like_count` to the y axis, and then display the data for each twitter user 
using geom_point. Since some users may have tweeted multiple times, we will 
calculate `average_like_count` per tweet for each user, and use that number in 
place of the actual `like_count` variable. This means for users who only tweeted 
once, we will use the like count for that tweet, while for users who tweeted 
multiple times, we will use the average like count across all of their challenge 
tweets. We chose to focus on individual users since in the previous 
visualization we were looking into cumulative tweets, on a non per-user basis. 
This way, for this question, we will be able to gauge Twitter engagement in the 
Dubois challenge on a per user basis, marking a contrast between our questions.
Then, we will use color mapping to map the verification status of the tweet 
author to the colors of the points, such that viewers can easily distinguish 
between the two groups (if the groups are not distinguishable, another option is 
to facet by verification status - we will make a choice about this after seeing 
how the data looks). Further, we'll display a geom_smooth regression line for
verified and unverified users (if these lines become visually distracting, we 
will reconsider using them). With these lines, we'll be able to examine the 
interaction between verification and followers and its effect on the number of 
likes a tweet can generate.

We believe that by taking the various aforementioned variables into account, our
data analysis and visualizations will be comprehensive and take full advantage 
of the data set. 